---
header-includes:
  - \usepackage{atkinson}
  - \renewcommand\familydefault{\sfdefault}
  - \usepackage[T1]{fontenc}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{fancyhdr}
  - \usepackage{makecell}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{lastpage}
  - \usepackage{lipsum}
  - \pagestyle{fancy}
  - \fancyhead[C]{Fiscal 20`r params$fy` Operating Budget Surplus/Deficit Projection}
  - \fancyhead[R]{Quarter `r params$qt`}
  - \fancyfoot[C]{\footnotesize Page \thepage\, of\, \pageref*{LastPage}}
  - \renewcommand{\headrulewidth}{0pt}


---
classoption: landscape
geometry: left=.25in,right=.25in,top=.7in,bottom=.7in
header-includes:
- \usepackage{helvet}
- \renewcommand\familydefault{\sfdefault}
- \usepackage[T1]{fontenc}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{fancyhdr}
- \usepackage{makecell}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{lastpage}
- \usepackage{lipsum}
- \pagestyle{fancy}
- \fancyhead[C]{Fiscal 20`r params$fy` Operating Budget Surplus/Deficit Projection}
- \fancyhead[R]{Quarter `r params$qt`}
- \fancyfoot[C]{\footnotesize Page \thepage\, of\, \pageref*{LastPage}}
- \renewcommand{\headrulewidth}{0pt}
output:
  pdf_document: null
  latex_engine: xelatex
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

options(knitr.table.format = "latex",
        knitr.kable.NA = '')
```

### By Pillar

```{r, fig.align = "center"}

chiefs_table %>%
  mutate(`Surplus/Deficit` = `YTD Exp` - `Q3 Projection`) %>%
  bookHelpers::format_table_numbers() %>%
  kable(booktabs = TRUE, longtable = TRUE, align = c('l', rep('r', 4))) %>%
  row_spec(0,  bold = TRUE) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 10)
```

```{r, fig.align = "center", out.width = '60%'}
pillar <- chiefs_table %>%
  group_by(`Pillar Name`) %>%
  summarize_if(is.numeric, sum)

pillar %>%
  select(label = `Pillar Name`, value = `Q3 Projection`) %>%
  arrange(label) %>%
  bookHelpers::format_plot(
    type = "pie", set_scale = "m", format = "percent", pie_total = TRUE, margin_b = 20,
    margin_l = 10, margin_r = 5, margin_t = .5, font_size = 14) %>%
  bookHelpers::export_plotly("pillars", width = "950", height = "500")
```
<!-- \newpage -->
```{r}
# vline <- function(x = 0, color = "black") {
#   list(
#     type = "line",
#     y0 = 0,
#     y1 = 1,
#     yref = "paper",
#     x0 = x,
#     x1 = x,
#     line = list(color = color)
#   )
# }
#
# df <- chiefs_report %>% filter(`Service` == "AGENCY TOTAL") %>%
#   select(`Agency`, `Q3 Surplus/Deficit`) %>%
#   rename(label = `Agency`, value = `Q3 Surplus/Deficit`)
#
# df$value <- as.numeric(df$value)
  # mutate(across(value, ~replace_na(.x,0))) %>%
  # format_number(value, negative_parens = FALSE, dollar_sign = FALSE, suffix = "none", scale = NULL)
#
# fig <- plot_ly(x = ~df$value, y = ~df$label, type = "bar", orientation = "h",
#                #text = paste(round(df$value/1000, 2), "K"),
#                text = df$value,
#                #textposition = 'outside',
#                color = ~df$value > 0,
#                colors = c("orange", "navy"))
#
# fig <- fig %>% layout(yaxis = list(title = "", showgrid = FALSE, showline = FALSE, showticklabels = TRUE),
#                       xaxis = list(title = "Surplus/Deficit"
#                                    #,range = c(min(df$value), max(df$value)*1.15)
#                                    ),
#                       #shapes = list(vline(0.0)),
#                       showlegend = FALSE,
#                       title = "Quarterly Surplus/Deficit by Agency")
#
# fig %>% export_plotly("quarterly_agency_overview", format = ".pdf")
```
<!-- \newpage -->
```{r, fig.align = "center", fig.height=2}

# plot <- pillar %>% filter(`Pillar Name`=="Building Public Safety") %>%
#   select(`FY20 Actual`, `FY21 Actual`, `Total Budget`, `Q3 Projection`)

# plot <- plot %>% t()%>%
#   as.data.frame() %>%
#    rownames_to_column %>%
#   mutate(diff = V1 - lag(V1, default = first(V1)))
#
# fig <- plot_ly(x = ~plot$rowname, y = ~plot$V1, type = "bar", #mode = "text",
#                text = ~plot$V1,
#                textposition = "outside",
#                text_template = "%{text:$,s}")
#
# fig <- fig %>% layout(title = "Building Public Safety Quarterly Projection",
#          xaxis = list(title = ""),
#          yaxis = list(title = ""),
#          annotations = list(x = plot$rowname,
#                             y = plot$V1,
#                             text = paste("Difference: ", plot$diff),
#                             xref = "x",
#                             yref = "y",
#                             showarrow = FALSE,
#                             ax = 20,
#                             ay = -20))
#

# fig %>% bookHelpers::export_plotly("pillars_public_safety", width = "950", height = "500")
  # bookHelpers::format_plot(
  #   "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 1200000000,  margin_b = 50,
  #   bar_anno_col = "Q3 Surplus/Deficit",
  #   bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>%
  # bookHelpers::export_plotly("pillars_public_safety", width = "950", height = "500")
```

<!-- \newpage -->
<!-- ```{r, fig.align = "center", fig.height=2} -->
<!-- pillar %>% filter(`Pillar Name`=="Prioritizing Our Youth") %>% -->
<!--   select(label = -`YTD Exp`) %>% -->
<!--   bookHelpers::format_plot( -->
<!--     "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 500000000,  margin_b = 50,  -->
<!--     bar_anno_col = "Q2 Surplus/Deficit",  -->
<!--     bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>% -->
<!--   bookHelpers::export_plotly("pillars_youth", width = "950", height = "500") -->
<!-- ``` -->
<!-- \newpage -->

<!-- ```{r, fig.align = "center", fig.height=2} -->
<!-- pillar %>% filter(`Pillar Name`=="Clean and Healthy Communities") %>% -->
<!--   select(label = -`YTD Exp`) %>% -->
<!--   bookHelpers::format_plot( -->
<!--     "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 400000000,  margin_b = 50,  -->
<!--     bar_anno_col = "Q2 Surplus/Deficit",  -->
<!--     bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>% -->
<!--   bookHelpers::export_plotly("pillars_clean", width = "950", height = "500") -->
<!-- ``` -->
<!-- \newpage -->

<!-- ```{r, fig.align = "center", fig.height=2} -->
<!-- pillar %>% filter(`Pillar Name`=="Responsible Stewardship of City Resources") %>% -->
<!--   select(label = -`YTD Exp`) %>% -->
<!--   bookHelpers::format_plot( -->
<!--     "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 225000000,  margin_b = 50,  -->
<!--     bar_anno_col = "Q2 Surplus/Deficit",  -->
<!--     bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>% -->
<!--   bookHelpers::export_plotly("pillars_resources", width = "950", height = "500") -->
<!-- ``` -->
<!-- \newpage -->

<!-- ```{r, fig.align = "center", fig.height=2} -->
<!-- pillar %>% filter(`Pillar Name`=="Equitable Neighborhood Development") %>% -->
<!--   select(label = -`YTD Exp`) %>% -->
<!--   bookHelpers::format_plot( -->
<!--     "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 100000000,  margin_b = 50,  -->
<!--     bar_anno_col = "Q2 Surplus/Deficit",  -->
<!--     bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>% -->
<!--   bookHelpers::export_plotly("pillars_equity", width = "950", height = "500") -->
<!-- ``` -->
<!-- \newpage -->

<!-- ```{r, fig.align = "center", fig.height=2} -->
<!-- pillar %>% filter(`Pillar Name`=="Other") %>% -->
<!--   select(label = -`YTD Exp`) %>% -->
<!--   bookHelpers::format_plot( -->
<!--     "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 400000000,  margin_b = 50,  -->
<!--     bar_anno_col = "Q2 Surplus/Deficit",  -->
<!--     bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>% -->
<!--   bookHelpers::export_plotly("pillars_other", width = "950", height = "500") -->
<!-- ``` -->
<!-- \newpage -->

<!-- ```{r, fig.align = "center"} -->
<!-- #troubleshoot -->
<!-- #pillar %>% filter(is.na(`Pillar Name`)) %>% -->
<!-- #  select(label = `Pillar Name`, `Total Budget`, `Q2 Projection`, `Q2 Surplus/Deficit`) %>% -->
<!-- #  bookHelpers::format_plot( -->
<!-- #    "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 50000000,  margin_b = 50,  -->
<!-- #    bar_anno_col = "Q2 Surplus/Deficit",  -->
<!-- #    bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>% -->
<!-- #  bookHelpers::export_plotly("pillars_other", width = "950", height = "500") -->
<!-- ``` -->
\newpage
```{r }
kable(chiefs_report, booktabs = TRUE, longtable = TRUE, align = c('l', 'l', rep('r', 8))) %>%
  collapse_rows(1:2, row_group_label_position = 'stack', longtable_clean_cut = FALSE,
              latex_hline = "major", headers_to_remove = 1:2) %>%
  row_spec(0,  bold = TRUE) %>%
  row_spec(nrow(chiefs_report) - 1,  hline_after = TRUE) %>%
  row_spec(c(nrow(chiefs_report), which(chiefs_report$Service == "Agency Total")), bold = TRUE) %>%
  column_spec(2, "2.5in") %>%
  column_spec(3:10, ".75in") %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 8)

```

\newpage

### By Ledger Account Summary

```{r Ledger Account Summary Table, fig.align = "center"}

ledger_summary <- import("G:/Analyst Folders/Sara Brumfield/_ref/Ledger Summary to Spend Category Map.xlsx") %>%
select(`Spend Category`, `Ledger Summary`)

ledger <- compiled %>%
  select(`Spend Category`, !!sym(paste0("FY", params$fy-2, " Actual")), !!sym(paste0("FY", params$fy-1, " Actual")),
         !!sym(paste0("FY", params$fy, " Budget")), !!sym(internal$col.proj), !!sym(internal$col.surdef)) %>%
  left_join(ledger_summary, by = "Spend Category") %>%
  group_by(`Ledger Summary`) %>%
  summarize_if(is.numeric, sum) %>%
  mutate(`Ledger Summary` = case_when(is.na(`Ledger Summary`) ~ "Blank",
                                      TRUE ~ `Ledger Summary`))

ledger %>%
  format_table_numbers() %>%
  kable(booktabs = TRUE, longtable = TRUE, align = c('l', rep('r', 5))) %>%
  row_spec(0,  bold = TRUE) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 10)
```

```{r Ledger Account Summary Graph, fig.align='center'}

ledger %>%
  select(label = `Ledger Summary`, `FY23 Budget`, !!sym(paste0("Q", params$qtr, " Projection")), !!sym(paste0("Q", params$qtr, " Surplus/Deficit"))) %>%
  arrange(label) %>%
  format_plot(
    type = "bar_group", set_scale = "m", title = "Quarterly Projection vs Budget", margin_t = 50, show_y = TRUE,
    set_min_y = -150000000, set_max_y = 1600000000, legend_y = -.1, bar_anno_y = 90000000,
    bar_anno_col = "Q2 Surplus/Deficit", bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>%
  # export_plotly("ledger", width = "950", height = "500")
  orca(file = "ledger.pdf", width = "800", height = "400")

include_graphics("ledger.pdf")

# ledger %>%
#   select(label = `Pillar Name`, `Total Budget`, `Q1 Projection`, `Q1 Surplus/Deficit`) %>%
#   arrange(`Pillar Name`) %>%
#   bookHelpers::format_plot(
#     "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 1000000000,  margin_b = 50,
#     bar_anno_col = "Q1 Surplus/Deficit", bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>%
#   bookHelpers::export_plotly("pillars", width = "950", height = "500")

```

<!-- \newpage -->

<!-- ### By Pillar -->

```{r, fig.align = "center"}
#
# pillar <- compiled %>%
#   mutate(`Pillar Name` = ifelse(is.na(`Pillar Name`), "Other", `Pillar Name`)) %>%
#   group_by(`Pillar Name`) %>%
#   summarize_if(is.numeric, sum)
#
# pillar %>%
#   bookHelpers::format_table_numbers() %>%
#   kable(booktabs = TRUE, longtable = TRUE, align = c('l', rep('r', 4))) %>%
#   row_spec(0,  bold = TRUE) %>%
#   kable_styling(latex_options = c("repeat_header"), font_size = 7)
#
# pillar %>%
#   select(label = `Pillar Name`, `Total Budget`, `Q1 Projection`, `Q1 Surplus/Deficit`) %>%
#   arrange(`Pillar Name`) %>%
#   bookHelpers::format_plot(
#     "bar_group", set_scale = "m", set_min_y = 0, set_max_y = 1000000000,  margin_b = 50,
#     bar_anno_col = "Q1 Surplus/Deficit", bar_anno_word_positive = " surplus", bar_anno_word_negative = " deficit") %>%
#   bookHelpers::export_plotly("pillars", width = "950", height = "500")


```
